\section{Related-work boundary}
The algebraic ingredients belong to angular-momentum recoupling and quantum-group theory \cite{biedenharnLouck1981,kirillovReshetikhin1989,kauffmanLins1994}.  Quantum $6j$ symbols also enter three-manifold state sums \cite{turaevViro1992}.  Large-label asymptotic formulas relate classical or quantum $6j$ symbols to Euclidean or non-Euclidean tetrahedra \cite{ponzanoRegge1968,roberts1999,taylorWoodward2005}.

The present result is different.  It takes no large-spin limit and infers no tetrahedral geometry from a phase.  It studies a finite explicit trigonometric q-Racah model near one fixed anchor.  The central object is the local analytic jet of a two-channel recoupling matrix, together with a finite Arb-certified regularity disk.  It is complementary to, not an extension of, the Ponzano--Regge asymptotic programme.

The use of analytic families and local power series is consistent with classical analytic perturbation theory \cite{kato1995}, although no eigenvalue perturbation theorem is required for the generator recurrence.  The tail estimate is a standard application of one-variable Cauchy bounds \cite{ahlfors1979}.  Rigorous numerical enclosure is provided by Arb midpoint-radius arithmetic \cite{johansson2017arb}.

\section{Claim-dependency ledger}
\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.28\textwidth}>{\raggedright\arraybackslash}p{0.23\textwidth}>{\raggedright\arraybackslash}p{0.36\textwidth}}
\toprule
Claim & Evidence type & Status\\
\midrule
q-Racah closure and jet recurrences & analytic proof & exact, arbitrary finite order conditional on regularity\\
283 carriers, 24 families, q-index ledger & exact integer enumeration & exact finite statement\\
low-order derivative agreement on 208 carriers & binary floating-point cross-validation & numerical through stated orders\\
uniform q-number separation & analytic bounds plus Arb enclosure & rigorous on the outer disk\\
uniform nonvanishing of $\omega$ & 192/256-bit Arb Taylor--Cauchy certificate & rigorous on $|z-\theta_0|\le\pi/1200$\\
maximal radius or unbounded-label stability & no certificate & not claimed\\
\bottomrule
\end{tabular}
\end{center}

\section{Reproducibility protocol}
The accompanying package contains:
\begin{itemize}[leftmargin=2em]
\item the finite q-$6j$ jet engine and frozen carrier-generation rules;
\item the exact 283-carrier supplementary list;
\item low-order cross-validation tests and certificates;
\item the Arb interval-conditioning builder, tests and certificate;
\item preregistration records for the confirmatory radius, precision and Taylor order;
\item machine-readable JSON outputs and theorem-audit response files.
\end{itemize}

The final release cycle will record the repository commit, Python, NumPy, pytest, python-flint and FLINT versions, deterministic commands, source and output hashes, generated-certificate equality and wall-clock runtime.  These release metadata must be generated from a clean checkout after the reviewed manuscript is committed.

\section{Claim firewall and limitations}
\subsection{Allowed bounded statement}
\begin{quote}
Inside the declared finite two-channel trigonometric q-Racah class, the exact recoupling matrix admits a recursive truncated-Taylor jet calculus.  Matrix derivatives through order three are cross-validated on 208 ordered carriers from families excluded by the frozen label-1-to-4 split.  All 283 algebraic carriers share an Arb-certified complex disk on which the critical q-number denominators, anchor-selected square-root branches and signed angular-speed logarithm remain regular.
\end{quote}

\subsection{Forbidden extrapolations}
The present evidence does not support:
\begin{itemize}[leftmargin=2em]
\item a theorem for all representations or unbounded labels;
\item an all-order software-validation result;
\item a universal compact descriptor replacing the finite q-Racah expression;
\item physical motion, time evolution, matter, mass or curvature;
\item a semiclassical geometric interpretation;
\item an absolute maximal-radius theorem.
\end{itemize}
Finite-label certification gives no automatic stability as $j\to\infty$; that regime requires a separate uniform asymptotic analysis.

\section{Conclusion}
A finite quantum $6j$ response problem that appears to require a new hand derivation at each order can be reorganized into one truncated-Taylor algebra.  The resulting coefficient calculus yields exact generator and holomorphic-logarithm recurrences.  The released implementation is cross-validated through matrix order three, while a separate outward-rounded Arb computation proves a common nonvanishing disk for the entire declared finite class.

The conceptual distinction is between explicit analytic evaluability and low-dimensional compression.  The local response is given by a finite analytic expression and is recursively evaluable, but it need not admit a small carrier-neutral descriptor.  Compression, higher-order software validation, larger carrier classes, asymptotic limits and physical interpretation remain separate obligations.
