\section{Introduction}
Quantum $6j$ symbols are finite recoupling coefficients associated with changes of basis between different parenthesizations of tensor products.  Their classical and quantum forms occur in angular-momentum theory, quantum-group representation theory and state-sum topology; see, for example, \cite{biedenharnLouck1981,kirillovReshetikhin1989,turaevViro1992}.  A separate body of work studies large-label or semiclassical asymptotics and their relation to tetrahedral geometry \cite{ponzanoRegge1968,roberts1999,taylorWoodward2005}.

The present paper asks a different and deliberately narrower question.  Fix a finite set of admissible doubled-spin labels and a regular trigonometric chamber in the deformation parameter $\theta$.  Can the local response of the corresponding finite recoupling matrix be generated recursively, validated independently on previously unseen representation families, and equipped with a common analytic-conditioning radius?

Three difficulties motivate the construction.
\begin{enumerate}[label=(\roman*)]
\item Direct hand differentiation of the finite quantum Racah expression becomes lengthy already at third order.
\item A low-dimensional regression descriptor need not reproduce the exact deformation response, even when the response itself is analytically computable.
\item Finite-order formulas are not useful uniformly unless denominators, square-root branches and the logarithmic angular-speed observable remain separated from singularities and zeros.
\end{enumerate}

The answer developed here has two parts.  First, the quantum Racah formula is evaluated in a truncated Taylor algebra.  This converts differentiation into coefficient arithmetic and gives a single recurrence for the matrix generator and its logarithmic scalar jet.  Second, the declared finite carrier class is certified on a common complex disk.  This produces a bounded result: the formal recurrence is valid at arbitrary finite order inside a regular chamber, while the software implementation and numerical validation are claimed only through the explicitly tested orders.

\subsection{Contributions}
The controlled contributions are:
\begin{enumerate}[leftmargin=2em]
\item a precise doubled-spin and channel convention for the declared two-channel class;
\item a recursive truncated-Taylor calculus for the finite quantum Racah expression;
\item a generator recurrence for $K=F'F^T$ and formal-logarithm recurrences for the angular-speed jet;
\item independent new-label validation of the first three matrix-response levels;
\item a common q-wall-safe and log-speed-nonvanishing disk for the full declared class;
\item a proof-family optimization yielding the confirmatory radius $R_{\mathrm{cert}}=0.1R_{\mathrm{wall}}$;
\item an explicit firewall separating these results from asymptotic geometry and physical interpretation.
\end{enumerate}

\subsection{Non-claims}
The paper does not claim:
\begin{itemize}[leftmargin=2em]
\item a continuum or semiclassical limit;
\item a Ponzano--Regge or Regge-curvature theorem;
\item a physical evolution law for $q$ or $\theta$;
\item a universal representation-only compression of the response;
\item an absolute maximal analytic radius;
\item validation beyond the declared finite two-channel class.
\end{itemize}
