\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools,bm}
\usepackage{booktabs,longtable,array}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue,
  pdftitle={Recursive Jet Calculus and Rigorous Uniform Conditioning for Finite Quantum 6j Recoupling Matrices},
  pdfauthor={A. A. Malachevsky},
  pdfsubject={Finite two-channel quantum 6j jet calculus with Arb-certified uniform conditioning},
  pdfkeywords={quantum 6j symbols, q-Racah, recoupling matrices, Taylor jets, Arb ball arithmetic}
}
\allowdisplaybreaks

\newtheorem{definition}{Definition}[section]
\newtheorem{lemma}[definition]{Lemma}
\newtheorem{proposition}[definition]{Proposition}
\newtheorem{theorem}[definition]{Theorem}
\newtheorem{corollary}[definition]{Corollary}
\newtheorem{remark}[definition]{Remark}
\newtheorem{assumption}[definition]{Assumption}

\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\HS}{\mathrm{HS}}
\newcommand{\ord}{\operatorname{ord}}
\newcommand{\Logh}{\operatorname{Log}}
\newcommand{\qnum}[1]{[#1]_q}
\newcommand{\qfac}[1]{[#1]_q!}
\newcommand{\sixj}[6]{\begin{Bmatrix}#1&#2&#3\\#4&#5&#6\end{Bmatrix}_{q}}
\newcommand{\dd}{\,\mathrm d}

\title{Recursive Jet Calculus and Rigorous Uniform Conditioning\\
for Finite Quantum $6j$ Recoupling Matrices\\
\large A bounded two-channel result with frozen new-label cross-validation}
\author{A. A. Malachevsky\\
Independent researcher\\
Boundary Compensation / BC-IDPR Programme}
\date{Version v0.1.1 reviewed manuscript, 16 July 2026}

\begin{document}
\maketitle

\begin{abstract}
We study a finite trigonometric quantum Racah model near the deformation anchor $q=e^{i\theta_0}$, $\theta_0=\pi/12$.  External and intermediate labels are doubled spins.  The scalar quantum $6j$ symbol and the associated two-channel recoupling matrix are defined explicitly in the paper, so no unstated modular-category normalization is imported.  The algebraic carrier class consists of 283 ordered four-tuples in 24 unordered external-label families; all q-number indices occurring in the finite formula are at most ten, below the first positive root-of-unity wall $[12]_q=0$ at the anchor.

The analytic core is a truncated-Taylor algebra lemma.  Products, quotients, square roots and finite sums in the exact finite q-Racah expression propagate recursively at arbitrary finite order on any regular simply connected chamber.  If
\[
F(\theta_0+h)=\sum_{r\ge0}F_rh^r,
\]
then the transpose-orthogonal recoupling generator $K=F'F^T$ satisfies
\[
K_r=\sum_{a=0}^{r}(a+1)F_{a+1}F_{r-a}^{T}.
\]
A holomorphic logarithm of the signed angular-speed jet gives recursive logarithmic derivatives.  The implementation is cross-validated through matrix derivative order three and logarithmic-speed derivative order two on a frozen held-out split of 208 ordered carriers in 15 families; the largest relative residuals for speed, logarithmic slope and logarithmic curvature are $2.03\times10^{-9}$, $1.85\times10^{-9}$ and $8.64\times10^{-9}$.

The uniform statement is certified with outward-rounded Arb ball arithmetic.  At both 192 and 256 bits, an order-50 Taylor--Cauchy enclosure proves for all 283 declared carriers that
\[
|\omega_J(z)|\ge 0.1602526414821766
\qquad
\text{whenever }|z-\theta_0|\le \pi/1200.
\]
Thus the anchor-selected square-root branches and the holomorphic logarithm of the signed angular speed are regular on one common disk.  The result is finite-label and local in the deformation parameter.  It makes no large-label, continuum, geometric-gravity or physical-dynamics claim.
\end{abstract}

\paragraph{Keywords.}
quantum $6j$ symbols; trigonometric q-Racah formula; recoupling matrices; truncated Taylor algebra; analytic jets; Cauchy estimates; Arb ball arithmetic; computer-assisted proof.

\paragraph{Software repository.}
\href{https://github.com/AIDevelopersMonster/boundary-compensation}{AIDevelopersMonster/boundary-compensation}

\paragraph{Author responsibility note.}
The author is the sole responsible scientific decision maker.  AI-assisted tools may have been used for technical drafting, structuring, consistency checks, software scaffolding and LaTeX preparation.  AI-assisted tools are not authors or coauthors.

\tableofcontents

\input{sections/01_introduction.tex}
\input{sections/02_conventions_and_racah.tex}
\input{sections/03_recursive_jet_calculus.tex}
\input{sections/04_independent_validation.tex}
\input{sections/05_uniform_conditioning.tex}
\input{sections/06_boundary_reproducibility_conclusion.tex}
\input{sections/07_appendices.tex}
\input{references.tex}
\end{document}
